Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-10 paper/main.tex
[issue 0.3, 1.2, 2.7] shorten sections more

In the end, we have 17,344 stars and 47,656 galaxies available
for the training and testing processes.
The apparent magnitudes range from $10.7 < r < 23.1$,
and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
\sout{
The $ugriz$ color-color space of the sample is plotted in
Figure~\ref{fig:sdss_color_color}.
}
We randomly split the objects into training, held-out validation,
and blind test sets of size 40,000, 10,000, and 15,000, respectively.
We note that cross-validation is often avoided in deep learning
in favor of hold-out validation,
since cross-validation is computationally expensive.
We also note that we perform a blind test, and the test set is not used in any
way to train or calibrate the algorithms.
The first two panels of Figure~\ref{fig:sdss_mag} show the number of objects
and the fraction of stars in the test set as functions of $r$-band magnitude.
Similarly, Figure~\ref{fig:sdss_g_r} shows the number of objects and the
fraction of stars in the test set as functions of $g-r$ color.
The normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set,
and they are nearly indistinguishable when overlapped.
We do not show the distributions for the training and validation sets in
Figures~\ref{fig:sdss_mag} and \ref{fig:sdss_g_r} to avoid cluttering the
plots.

@@

In the end, we have 8,545 stars and 57,843 galaxies available
for the training and testing processes.
The apparent magnitudes range from $13.9 < r < 25.6$,
and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
\sout{
The $ugriz$ color-color space of the sample is plotted in
Figure~\ref{fig:clens_color_color}.
}
We randomly split the objects into training, held-out validation, and
blind test sets of size 40,000, 10,000, and 13,278, respectively.
Figures~\ref{fig:clens_mag} and \ref{fig:clens_g_r} show the distribution
of objects in the test set as functions of $i$-band magnitude and $g-r$ color.
We do not show the distributions for the training and validation sets,
since the normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set.

@@

Many deep learning models use feedforward neural network architectures with multiple layers,
where each neuron in one layer is connected to the neurons of the subsequent layer.
A schematic representation is shown in Figure~\ref{fig:neuron_b}.
All layers except the input and output layers are conveniently called hidden layers.
With multiple hidden layers, deep neural networks can model complex nonlinear
relationships, and they have had great success in multimedia tasks where humans traditionally
outperformed computers, such as speech recognition, language processing, and image classification.

@@

%The gradients in \ref{eq:gradient_descent} can be computed using the
%\textit{backpropagation} procedure~\citep{rumelhart1988learning},
%which is nothing more than an application of the chain rule for derivatives.
%The derivative of the loss function with respect to the input of a unit can be
%computed by working backwards from the gradient with respect to the output of
%the unit.
%At the output layer, the derivative of the loss function with respect to the
%output is given by
%\begin{align}
%  \frac{ \partial L }{ \partial y_i } &= y_i - \hat{y}_i \\
%  \frac{ \partial L }{ \partial x_i } &=
%    \frac{ \partial L }{ \partial y_i }
%    \frac{ \partial y_i }{ \partial x_i }.
%\end{align}
%At each hidden layer, the derivative of the loss function with respect to the
%output of each unit is a weighted sum of the derivatives with respect to the
%inputs of the subsequent layer,
%\begin{align}
%  \frac{ \partial L }{ \partial y_j } &=
%    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}   \\
%  \frac{ \partial L }{ \partial x_j } &=
%    \frac{ \partial L }{ \partial y_j }
%    \frac{ \partial y_j }{ \partial x_j }.
%\end{align}
%Finally, once the gradients $\partial L / \partial x_j$ have been
%computed, it is straightforward to compute the gradients for the weight,
%\begin{equation}
%\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
%\end{equation}

>>>>

In the end, we have 17,344 stars and 47,656 galaxies available
for the training and testing processes.
The apparent magnitudes range from $10.7 < r < 23.1$,
and the galaxies in this sample have a mean redshift of $z \sim 0.36$.
\sout{
The $ugriz$ color-color space of the sample is plotted in
Figure ?%~\ref{fig:sdss_color_color}.
}
We randomly split the objects into training, held-out validation,
and blind test sets of size 40,000, 10,000, and 15,000, respectively.
We note that cross-validation is often avoided in deep learning
in favor of hold-out validation,
since cross-validation is computationally expensive.
We also note that we perform a blind test, and the test set is not used in any
way to train or calibrate the algorithms.
The first two panels of Figure~\ref{fig:sdss_mag} show the number of objects
and the fraction of stars in the test set as functions of $r$-band magnitude.
Similarly, Figure~\ref{fig:sdss_g_r} shows the number of objects and the
fraction of stars in the test set as functions of $g-r$ color.
The normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set,
and they are nearly indistinguishable when overlapped.
We do not show the distributions for the training and validation sets in
Figures~\ref{fig:sdss_mag} and \ref{fig:sdss_g_r} to avoid cluttering the
plots.

@@

In the end, we have 8,545 stars and 57,843 galaxies available
for the training and testing processes.
The apparent magnitudes range from $13.9 < r < 25.6$,
and the galaxies in this sample have a mean redshift of $z \sim 0.59$.
\sout{
The $ugriz$ color-color space of the sample is plotted in
Figure ?%~\ref{fig:clens_color_color}.
}
We randomly split the objects into training, held-out validation, and
blind test sets of size 40,000, 10,000, and 13,278, respectively.
Figures~\ref{fig:clens_mag} and \ref{fig:clens_g_r} show the distribution
of objects in the test set as functions of $i$-band magnitude and $g-r$ color.
We do not show the distributions for the training and validation sets,
since the normalized kernel density estimate distributions for the training
and validation sets are almost identical to those of the test set.

@@

Many deep learning models use feedforward neural network architectures with multiple layers,
where each neuron in one layer is connected to the neurons of the subsequent layer.
A schematic representation is shown in Figure~\ref{fig:neuron_b}.
All layers except the input and output layers are conveniently called hidden layers.
\sout{
With multiple hidden layers, deep neural networks can model complex nonlinear
relationships, and they have had great success in multimedia tasks where humans traditionally
outperformed computers, such as speech recognition, language processing, and image classification.
}

@@

\sout{
The gradients in Equation~\ref{eq:gradient_descent}
can be computed using the \textit{backpropagation} procedure%~\citep{rumelhart1988learning},
which is nothing more than an application of the chain rule for derivatives.
The derivative of the loss function with respect to the input of a unit can be
computed by working backwards from the gradient with respect to the output of
the unit.
At the output layer, the derivative of the loss function with respect to the
output is given by
}

\sout{$
  \frac{ \partial L }{ \partial y_i } = y_i - \hat{y}_i
$}
\sout{$
  \frac{ \partial L }{ \partial x_i } =
    \frac{ \partial L }{ \partial y_i }
    \frac{ \partial y_i }{ \partial x_i }.
$}

\sout{
At each hidden layer, the derivative of the loss function with respect to the
output of each unit is a weighted sum of the derivatives with respect to the
inputs of the subsequent layer,
}
\sout{$
  \frac{ \partial L }{ \partial y_j } =
    \sum_{i} w_{ji} \frac{ \partial L }{ \partial x_i}
$}
\sout{$
  \frac{ \partial L }{ \partial x_j } =
    \frac{ \partial L }{ \partial y_j }
    \frac{ \partial y_j }{ \partial x_j }.
$}

\sout{
Finally, once the gradients $\partial L / \partial x_j$ have been
computed, it is straightforward to compute the gradients for the weight,
}
\sout{$
\frac{\partial L}{\partial w_{jk}} = y_k \frac{\partial L}{\partial x_j}.
$}
